Naive Bayes Workflow

### 2019-02-25 docs/hiding/Check_in_Jan_14.Rmd
Web site update

---
title: "Feb 4 Check-In"
author: "Dan Johnson"
date: "2/3/19"
output: html_document
---

@@

#New ideas From FLC Meeting #6

Need help with:

Coding issues

*  How to ID, prune unneeded packages. NO SIMPLE SOLUTION. Cut and test seems best.

*  When I join columns in correlation analysis, if a word is MISSING from **any subset** the data for that word is pruned from the full dataset. I am losing the unique words this way. 
    +  Assume the NA would blow up correlations, which is why it is done this way.
    +  Need to figure out how to join without pruning, then find the UNIQUE words.

Post-Processing issues. Use broom package

*  How to calculate the value automatically in the Naive Bayes final step. Data post-processing. I have stable code for my binomial naive Bayes classifier, and I am screening different permutations to see what the best approach is to refining the model. There is one step I cannot figure out how to code though.My primary output is a cross-comparison table showing what fraction of the test set comments is correctly identified. Adding the counts diagonally and dividing by the total number of test cases gives me the overall accuracy.The table has all of the data that I want to use for other calculations, but I cannot figure out how to either: 1) call values from the table, or 2) pull

 Output issues

*  How to take the Excel/csv tables I have for permutations of naive Bayes, Pearson's r, and bring them in for display in summary page. broom

Add to My Code:

*  shell(cmd, shell, flag = "/c", intern = FALSE, wait = TRUE,
      translate = FALSE, mustWork = FALSE, ...) runs UNIX commands
https://www.rdocumentation.org/packages/base/versions/3.4.0/topics/shell

*  Using csvy format. R supports .csvy using csvy package and read_csvy() and write_csvy()
Reference Sites:

*  Using broom for cleanup
https://cran.r-project.org/web/packages/broom/vignettes/broom.html

Packages to Explore:

*  fs. https://fs.r-lib.org/index.html

fs provides a cross-platform, uniform interface to file system operations. It shares the same back-end component as nodejs, the libuv C library, which brings the benefit of extensive real-world use and rigorous cross-platform testing. fs functions are divided into four main categories:

    path_ for manipulating and constructing paths
    file_ for files
    dir_ for directories
    link_ for links
fs is designed to work well with the pipe, though because it is a minimal-dependency infrastructure package it doesn’t provide the pipe itself. You will need to attach magrittr or similar. fs functions also work well in conjunction with other tidyverse packages, like dplyr and purrr.

*  Best practices when writing R code
https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/

#File Management

```{r}
headlines2 <- read_docx("R_0eqZDDQ0nG2obuh_text.docx") %>% head(9)
View(headlines2)
```

R can manipulate files and folders. This is a primer:
http://theautomatic.net/2018/07/11/manipulate-files-r/

Get, change working directory
Create files of any type based on extension
Copy a file or folder
List files in a directory, including by sub-type
Use rowbind to join file contents
Get snapshot data
Remove files, folders
Check for files, folders
Get the basenames for files, folders
Get file extensions
Call shell to open the file
Move a file

# read in all the CSV files
all_data_frames <- lapply(list.files(pattern = ".csv"), read.csv)

# stack all data frames together
single_data_frame <- Reduce(rbind, all_data_frames)

Default
draft
General_workflow
initial_exploration
Naive_bayes_V2b, r, yn
pre_work
project
questions
reference_tables
course_notes

ta_comments_FLC
Text Classifier Models
Random_forest_notes
Latent_dirichlet_allocation_notes
  folder=data
    codebook_for_comments.md
    code_column_names.md
    TA_and_Student_IDs.csv
    ID_lookup.csv
  folder=docs_and_notes
    Grading Criteria.rmd
    Raw_data_structure.rmd

###Planned Project Pages
It may seem excessive, but my thinking is that:
1. Our group is the first so should establish some guidelines for creating tools.
2. Work I put in here translates over to the final, shared product for NSF project.

*  toc = Table of Contents
*	 project = Project Summary

*	 Background
    +  Theoretical background on text classifiers
    +  Practical background on project challenges

*	 Project Methods and Guides
    +  Anonymizing Data
    +  Standard Workflow
    +  Reference Tables
        -  Recoding lists
    +  Project Codebook

*  Pages template:
    +  Page Goals
    +  Page Overview
    +  Page Content

*  Initial Exploration
    +  Data Processing
    +  Preliminary Visualization

*  Deeper Analyses
    +  Categorical Naive Bayes
        -  Baseline cNB
        -  Randomized cNB
        -  Binary cNB
        -  Summary of cNB Findings

***
***

#Jan 14 Check-In, and New ideas From FLC Meeting #5

@@

@@

@@

1.  Randomization. Does the straight split I used bias the data? 
  Comment: YES, so instead use set.seed to pick more randomized dataset.

@@

>>>>

---
title: "Jan 14 Check-In"
author: "Dan Johnson"
date: "1/29/19"
output: html_document
---

@@

#New ideas From FLC Meeting #5

@@

Solved the data confidentiality problem. Turned out to be easier and more secure to do outside of R.

Manipulating the column vectors.
  Suggested: I need to recode some values to simplify. 
Second, in this same correlation analysis, I would recommend recoding the values in the `code.subject` column. You have some type of error there and I tend to avoid calling values such as "2. Writing Quality" as they tend make code more difficult to visually parse (and therefore debug) and it's also easy to get something wrong with the value (even though it seems that you've directly copied and pasted the values to double check).

For recoding comment labels, this is what I plan to use:

Recoding Comment.subject
0_null
1_basic
2_writing
3_technical
4_logic
5_exposition
6_misconduct
7_administrative
8_nobasis
9_split
10_context
11_flag
12_narrative
13_sciname

Recoding Comment.structure
0_null
1_pointer
2_copyedit
3_general
4_specific
5_rationale
6_holistic
7_idiomatic
8_nobasis

Calculation and plotting correlations and log-odds pairs is working (except for broken parts that recoding should solve hopefully.)

@@

Have an operational categorical naive Bayes workflow that can perform analysis using 1-, 2-, or 3-grams.

@@

1.  Randomization. Does the straight split I used bias the data? 
  Comment: YES, so instead use the following code to pick more randomized dataset.

```{r}
library(dplyr)
set.seed(1234) #randomization will be same set each time
train <- sample_frac(mtcars, .8) #sets how many are in random training set
test <- setdiff(mtcars, train) #chooses non-training for test set
```

@@

    FLC - Data Analysis (AB)

My project is still taking shape (and isn't yet really research, per se), but a few things I've been working on:

    Project Updates - Updating some content on my Project page
    New Page - Learning Analytics. This is a proposal I have had accepted for an April conference, and I am hoping our group might help me develop some of my thinking on the issue.
    Course Notes - I haven't kept up with note taking in this space, but added some of the detail from my work during Session 4. I am looking forward to engaging more actively with this space during our actual sessions, and I am interested in hearing about others' thoughts on this process.

While there are many more updates I hope to make this term, I wanted to share some of this work. You might also check out Dan's page (as his is more robust than mine).

To-Do

    Prepare to present on your progress at Monday's Session
    Update your website (or have a plan to do so).
    Raise questions (technical or otherwise) in the TLC discussion board space.

I am looking forward to seeing everyone on Monday (assuming we aren't snowed out).

2.  How to ID, prune unneeded packages.

3.  When I join columns in correlation analysis, when a word is MISSING from **any subset** the data for that word is pruned from the full dataset. I am losing the unique words this way. Need to figure out how to join without pruning.

6.  Broken correlation analyses. I have a problem buried in the coded data that is throwing an error in correlations. Jerid recommended recoding the values in the `code.subject` column.

### 2019-02-25 docs/hiding/Naive_bayes_notes3.Rmd
Web site update

##Starting Version for Bigrams, Trigrams
The original code is in rows 22 to ~235 of of Version 2 of this document. Works as of 12/18/2018. This is modified for n-grams instead of single words.

@@

```{r}
##Text Transformation using "tm" package in R to create a volitile coprus that contains the "text" vector from our data frame.
sms_corpus2 <- VCorpus(VectorSource(sms_raw2$text))

#Convert to all lower case letters with "tm_map"" funtion in R, then use the "content_transformer" function to transform the text.
sms_corpus_clean2 <- tm_map(sms_corpus2, content_transformer(tolower))

#This removes numbers. **May not want to do.**
sms_corpus_clean2 <- tm_map(sms_corpus_clean2, removeNumbers)

#Stopword removal. **One of variables to test out.**
sms_corpus_clean2 <- tm_map(sms_corpus_clean2, removeWords, stopwords())

#Remove punctuation as well using the "removePunctuation" function. Try not doing this. Removes evidence of questions.
sms_corpus_clean2 <- tm_map(sms_corpus_clean2, removePunctuation)
```

Final step in text mining is to remove white spaces. 
```{r}
sms_corpus_clean2 <- tm_map(sms_corpus_clean2, stripWhitespace)
```

Code to inspect a line of text.
```{r}
as.character(sms_corpus_clean2[[3]])
```

#Single word tokenization
Block tokenizes using the "DocumentTermMatrix" function. This creates a matrix in which the rows indicate documents (SMS messages in this case) and the columns indicate words. It should be noted that the "DocumentTermMaxtrix" function has the power to do all of the text mining above in one command. The "tidy" command is a hack that makes it easier to inspect the document terms matrix.
```{r}
sms_dtm2 <- DocumentTermMatrix(sms_corpus_clean2)
sms_dtm2_tidy <- tidy(sms_dtm2)
```

#N-gram tokenization
This code block uses tm's NLP functions to generate n-grams from the full corpus of TA comments

@@

NLP_Tokenizer <- function(x) {
      unlist(lapply(ngrams(words(x), 2), paste, collapse = " "), use.names = FALSE)
}

sms_dtm2_bigrams <- TermDocumentMatrix(sms_corpus_clean2, control=list(tokenize = NLP_Tokenizer))

inspect(sms_dtm2_bigrams)

@@

This should build an inspectable doc-terms matrix using n-grams described in "sms_dtm2_bigrams"
```{r}
sms_dtm2_bigrams_tidy <- tidy(sms_dtm2_bigrams)

#sms_dtm_trigram <- DocumentTermMatrix(sms_corpus_clean2, control = list(tokenize=tdm_NLP))
#sms_dtm_trigram_tidy <- tidy(sms_dtm_trigram)
```

Data Tables for Analysis
sms_dtm2
sms_dtm2_bigrams
sms_corpus_clean2

**Along the way I picked up this quick code block for generating 2-grams and 3-grams from full corpus of TA comments using the "corpus"" library**

```{}
library(corpus)
corpus <- sms_corpus_clean2 
text_filter(corpus)$drop_punct==TRUE
term_stats(corpus, ngrams = 2:3)
```

Data Tables for Analysis
sms_dtm2
sms_dtm2_bigrams
sms_dtm_trigram

```{}
**OPTION**
library(tm); library(tau);

@@

  tdm <- TermDocumentMatrix(crude, control = list(tokenize = BigramTokenizer))
  inspect(removeSparseTerms(tdm[, 1:10], 0.7))
```
####\

@@

This code assumes comments are random. **Probably want to try randomizing them.**
```{r}
sms_dtm_train2 <- sms_dtm2_bigrams[1:6846, ]
sms_dtm_test2 <- sms_dtm2_bigrams[6847:9129, ]
```

Data Tables for Analysis
sms_dtm2 = sms_dtm2_bigrams,  sms_dtm_trigram
sms_dtm_train2, _test2
sms_train_labels2, sms_test_labels2

Data Tables for Analysis
sms_dtm2
sms_dtm2_bigrams
sms_corpus_clean2

Limit our Document Term Matrix to only include words in the sms_freq_vector. We want all the rows, but we want to limit the column to these words in the frequency vector.
```{r}
sms_dtm_freq_train2 <- sms_dtm_train2[ , sms_freq_words2]

sms_dtm_freq_test2 <- sms_dtm_test2[ , sms_freq_words2]
```

This code assumes comments are random. **Probably want to try randomizing them.**
```{}
sms_dtm_train2 <- sms_dtm2[1:6846, ]
sms_dtm_test2 <- sms_dtm2[6847:9129, ]
```

>>>>

##Starting Version 1.0
Rows 22 to ~235 of this code are original starting version. Works as of 12/18/2018

@@

Perform "stemming" to the text data to strip the suffix from words. **Try NOT doing this.** 
```{r}
sms_corpus_clean2 <- tm_map(sms_corpus_clean2, stemDocument)
```

**Original Version**
Performs tokenization using the "DocumentTermMatrix" function. This creates a matrix in which the rows indicate documents (SMS messages in this case) and the columns indicate words. It should be noted that the "DocumentTermMaxtrix" function has the power to do all of the text mining above in one command.
```{r}
sms_dtm2 <- DocumentTermMatrix(sms_corpus_clean2)
sms_dtm2_tidy <- tidy(sms_dtm2)
```

**Quick code block to generate 2-grams and 3-grams from full corpus of TA comments**

```{r}
library(corpus)
corpus <- sms_corpus_clean2 
text_filter(corpus)$drop_punct==TRUE
term_stats(corpus, ngrams = 2:3)
```

text.corpus = sms_corpus_clean2

**This code block used tm's NLP generate n-grams from full corpus of TA comments**

@@

NLPtrigramTokenizer <- function(x) {
      unlist(lapply(ngrams(words(x), 3), paste, collapse = " "), use.names = FALSE)
}

tdm_NLP <- TermDocumentMatrix(sms_corpus_clean2, control=list(tokenize = NLPtrigramTokenizer))

inspect(tdm_NLP)

@@

This should build a doc-terms matrix tokenize using n-grams 
```{r}
library(topicmodels)
library(RWeka)
corpus <- sms_corpus_clean2 
text_filter(corpus)$drop_punct==TRUE
term_stats(corpus, ngrams = 2:3)

sms_dtm_bigram <- DocumentTermMatrix(sms_corpus_clean2, control = list(tokenize=term_stats))
sms_dtm_bigram_tidy <- tidy(sms_dtm_bigram)
```

**OPTION**
library(tm); library(tau);

@@

  tdm <- TermDocumentMatrix(crude, control = list(tokenize = BigramTokenizer))
  inspect(removeSparseTerms(tdm[, 1:10], 0.7))

@@

### 2019-02-25 docs/hiding/Naive_bayes_notes4.Rmd
Web site update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Summary
This notebook documents a basic workflow for applying a naive Bayes model to terms in TA comments. I based it on a tutorial [https://rpubs.com/Billyhansen6/318412](located here). This is quoted from Hansen's original tutorial:
>The objective of this project is to classify SMS messages as spam or ham (not spam). A Naive Bayes classifier approach will be used. This example is taken from chapter 4 of Machine Learning with R, Second Edition"

>An example of the conditional probability that will be computed is as follows:

$$P(Spam|Hospital) = P(Hospital|Spam)P(Spam)/P(Hospital)$$

>which is the formula for determining the probability that a message is spam given that it contains the word "Hospital" in the message.

Lines ~30-205 are the baseline version of the workflow using single words. It correctly classifies comments in the top 4 sub-categories  ~79% of the time. While that is close to minimum acceptable inter-rater reliability of two human readers, it is well below my goal of >95% for use in routine automated analysis.

Lines ~208-290 describe an alternative method using n-grams. When I tested this approach using 2-grams, classification was slightly worse, at 68.3% correct.

Lines ~295-335 show how to use word clouds to visualize single word frequencies. I did not find this approach very useful.

To keep this code clean for now I will run various permutations in a scratch version, then summarize findings starting on line #345. In these subsequent iterations I will evaluate:

*  Different text pre-processing strategies: stemmed versus unstemmed, numbers removed vs. not, etc.
*  Using n-grams rather than single words
*  Making pair-wise comparison versus comparing multiple groups simultaneously
*  Modifying the variables in the NB analysis itself.

Finally, there are several things still missing or needed for this workflow:

*  How to feed a text dataset in, and get a table of the predicted categories back out.
*  How to store the values from the Bayes prediction table so I can use them in calculations rather than type them in by hand.
*  How to randomize which comments are used for training, testing datasets.

@@

##Baseline Version 1.0 of Naive Bayes (NB) Protocol
###Initial Data Input
```{r}
#Read in TA comments from CSV file.
base_data <- read_csv(file='data/coded_full_comments_dataset_Spring18anon.csv')

@@

The OPTIONAL data transforms using "tm_map"" and "content_transformer" functions. Switch between "{r}" and "{}" to turn a transformation block off or on.
```{r}
#Convert to all lower case letters.
comments_corpus_clean <- tm_map(comments_corpus, content_transformer(tolower))
```

@@

```{r}
#Remove punctuation using the "removePunctuation" function. 
#This step removes evidence of questions, so may remove data.
comments_corpus_clean <- tm_map(comments_corpus_clean, removePunctuation)
```

@@

Final prep and data check.
```{r}
#Final step removes white space from the document. This is NOT optional.
comments_corpus_clean <- tm_map(comments_corpus_clean, stripWhitespace)

#Look at an example of data.
as.character((comments_corpus_clean[[3]]))
```

@@

###Basic Tokenizer
This version uses the "DocumentTermMatrix" function to creates a matrix in which the rows indicate individual documents (individual TA comments) and the columns indicate presence or absence of the word that is the header for the column. Be careful not to confuse it with "TermDocumentMatrix", which transposes the matrix.

@@

###Data Preparation
Split data into 75% training and 25% testing sets, so that after Naive Bayes spam filter algorithm is built it can be applied to unseen data. 
```{r}
.75 * 9340 #Number of documents/rows in the dataset; product is #rows for training
.25 * 9340 #Product is #rows for testing set
```

@@

Calculate overall correct prediction rate.
```{r}
(42+454+1186+185)/23.35
```

***
##Modified Naive Bayes (NB) Method Using N-grams
The tokenizer command block above only works for single words. The block below uses tm's NLP commands to generate either 1-, 2-, or 3-grams with the same command. The only change needed is "#" in "(words(x), #)" below. For simplicity I left off all of the preparatory code up leading up to the final cleaned corpus.

@@

```{r}
.75 * 9340 #Number of rows in the dataset; product is #rows for training
.25 * 9340 #Product is #rows for testing set
```

This code assumes comments are random. **Probably want to try randomizing them.**
```{r}
comments_dtm_train <- comments_dtm_2gram[1:7005, ]
comments_dtm_test <- comments_dtm_2gram[7006:9340, ]
```

@@

```{r}
(34+214+1254+94)/23.35
```

***
***
####\

##Visualization
This code generates a wordcloud of the frequency of single words in the dataset using the package "wordcloud".
```{r}
wordcloud(comments_corpus_clean, max.words = 50, random.order = FALSE)
```

@@

@@

##Permutation Tests of Naive Bayes (NB) Method
Version 1.0 correctly identifies comment subcategories ~79% of the time when using single words, and 68.3% of the time when using 2-grams. Permutations to test:

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Summary
This notebook documents a basic workflow for applying a naive Bayes model to terms in TA comments. Rows ~30-200 are the initial version that I based on this tutorial [https://rpubs.com/Billyhansen6/318412]. Various permutation tests start around row #210.

@@

##Baseline Version 1.0 of Naive Bayes (NB) Protocol
Initial data input.
```{r}
#Read in TA comments from CSV file.
base_data <- read_csv(file='data/coded_full_comments_dataset_Spring18anon.csv')

@@

These are the OPTIONAL data transforms using "tm_map"" and "content_transformer" functions.
```{r}
#Convert to all lower case letters.
comments_corpus_clean <- tm_map(comments_corpus, content_transformer(tolower))
```

@@

```{r}
#Remove punctuation as well using the "removePunctuation" function. 
#This step removes evidence of questions, so may remove data.
comments_corpus_clean <- tm_map(comments_corpus_clean, removePunctuation)
```

@@

Final prep and data check.
```{r}
#Final step removes white space from the document. This is NOT optional.
comments_corpus_clean <- tm_map(comments_corpus_clean, stripWhitespace)
```

```{r}
#Look at an example of data.
as.character((comments_corpus_clean[[3]]))
```

@@

**Original Tokenizer**
This version uses the "DocumentTermMatrix" function to creates a matrix in which the rows indicate individual documents (individual TA comments) and the columns indicate presence or absence of the word that is the header for the column. Be careful not to confuse it with "TermDocumentMatrix", which transposes the matrix.

@@

###Data Preparation
Split data into 75% training and 25% testing sets, so that after Naive Bayes spam filter algorithm is built it can be applied to unseen data. 
```{r}
.75 * 9340 #Number of rows in the dataset; product is #rows for training
.25 * 9340 #Product is #rows for testing set
```

@@

```{r}
(42+449+1185+186)/2335
```

***
***

##Permutations of Naive Bayes (NB) Method
Version 1.0 correctly identify comment subcategories ~80% of the time. This is better than the inter-rater reliability of two human raters, but still low. This notebook documents tests of various permutations of the NB method including:

Data set converted to a volative corpus using "tm" library then transformed.
```{r}
#Create the volatile coprus that contains the "text" vector from data frame.
comments_corpus <- VCorpus(VectorSource(comments_raw$text))
print(comments_corpus)

The OPTIONAL data transforms using "tm_map"" and "content_transformer" functions.
```{r}
#Convert to all lower case letters.
comments_corpus_clean <- tm_map(comments_corpus, content_transformer(tolower))
```

```{r}
#Remove punctuation as well using the "removePunctuation" function. 
#This step removes evidence of questions, so may remove data.
comments_corpus_clean <- tm_map(comments_corpus_clean, removePunctuation)
```

Final prep and data check.
```{r}
#Final step removes white space from the document. This is NOT optional.
comments_corpus_clean <- tm_map(comments_corpus_clean, stripWhitespace)
```

```{r}
#Look at an example of data.
as.character((comments_corpus_clean[[3]]))
```

**Alternative Tokenizer For N-grams**
This code block uses tm's NLP commands to generate n-grams from full corpus of TA comments. It can create 1-, 2-, and 3-grams all with the same commands simply by changing "#" in "(words(x), #)" below.

@@

```{r}
.75 * 9129
.25 * 9129
```

This code assumes comments are random. **Probably want to try randomizing them.**
```{r}
comments_dtm_train <- comments_dtm_2gram[1:6846, ]
comments_dtm_test <- comments_dtm_2gram[6847:9129, ]
```

Save vectors labeling rows in the training and testing vectors
```{r}
comments_train_labels <- comments_raw[1:6846, ]$type
comments_test_labels <- comments_raw[6847:9129,]$type
```

@@

###Train Model, Predict, Evaluate
Use the e1071 package to implement Naive Bayes algorithm on the data, and predict whether a message is likely to be in group TWO, THREE, or FOUR. Evaluate the prediction with the actual data using a crosstable from the gmodels package.
```{r}
comments_classifier <- naiveBayes(comments_train, comments_train_labels)
comments_test_pred <- predict(comments_classifier, comments_test)
CrossTable(comments_test_pred, comments_test_labels, prop.chisq = FALSE, prop.t = FALSE, dnn = c('predicted', 'actual'))
```

```{r}
(39+219+1233+90)/2283
```

***
***

##Visualization
Create a wordcloud of the frequency of the words in the dataset using the package "wordcloud".
```{r}
wordcloud(comments_corpus_clean, max.words = 50, random.order = FALSE)
```

@@

***
***

**Permutation 1**
Did not remove numbers, did not remove stopwords or punctuation, did not stem the terms. Reduced word count limit from 5 to 4 for matrix word limit.

```{}
comments_freq_words <- findFreqTerms(comments_dtm_train, 4)
str(comments_freq_words)
```

This step raised accuracy for calling 3_Technical comments to 91.9%, but dropped overall accuracy to 79.0%.

***
***

**Permutation 2**
Removed stopwords, numbers and punctuation, but did not use stemming. Also dropped to comparing two groups. This approach raised the accuracy to:

*  87.7% for separating 2_writing and 3_technical. 
*  83.1% for separating 2_writing and 4_logic. 
*  91.2% for separating 3_technical and 4_logic.

```{r}
library(tidyverse)
library(tidytext)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(tm)
library(SnowballC)
library(wordcloud)
library(e1071)
library(gmodels)
library(readr)
```

```{r}
#Read in CSV file named "coded_full_comments_dataset_Spring18anon.csv".
base_data <- read_csv(file='data/coded_full_comments_dataset_Spring18anon.csv')

#Isolate rows to compare. 
comments_subset <- filter(base_data,code.subject=="3. Technical and Scientific"|code.subject=="4. Logic and Thinking") #|code.subject=="2. Writing Quality"

#Simplify coding terms
comments_raw[,1] <- ifelse(comments_raw[,1] == "3. Technical and Scientific", "3_Technical", ifelse(comments_raw[,1] == "4. Logic and Thinking","4_Logic", 99))# ifelse(comments_raw[,1] == ,99)))"2. Writing Quality", "2_Writing"

```{r}
##Text Transformation using "tm" package in R to create a volitile coprus that contains the "text" vector from our data frame.
comments_corpus <- VCorpus(VectorSource(comments_raw$text))
print(comments_corpus)

In order to standardize the messages, the data set must be tranformed to all lower case letters. The words "Free", "free", and "FREE" should all be treated as the same word. Use the "tm_map"" funtion in R, and use the "content_transformer" function to transform the text.
```{r}
comments_corpus_clean <- tm_map(comments_corpus, content_transformer(tolower))
```

Look at third message again to see if our data was transformed.
```{r}
as.character(comments_corpus[[3]])

as.character((comments_corpus_clean[[3]]))
```

This removes numbers. **May not want to do.**
```{r}
comments_corpus_clean <- tm_map(comments_corpus_clean, removeNumbers)
```

Stopword removal takes out words that appear often but don't contribute to our objective. These words include "to", "and", "but" and "or". **One of variables to test out.**
```{r}
comments_corpus_clean <- tm_map(comments_corpus_clean, removeWords, stopwords())
```

Remove punctuation as well using the "removePunctuation" function. **Try not doing this. Removes evidence of questions.**
```{r}
comments_corpus_clean <- tm_map(comments_corpus_clean, removePunctuation)
as.character((comments_corpus_clean[[3]]))
```

Perform "stemming" to the text data to strip the suffix from words. **Try NOT doing this.** 
```{}
comments_corpus_clean <- tm_map(comments_corpus_clean, stemDocument)
```

And now the final step in text mining is to remove white space from the document. 
```{r}
comments_corpus_clean <- tm_map(comments_corpus_clean, stripWhitespace)
```

```{r}
as.character(comments_corpus_clean[[3]])
```

Perform tokenization using the "DocumentTermMatrix" function. This creates a matrix in which the rows indicate documents (SMS messages in this case) and the columns indicate words. It should be noted that the "DocumentTermMaxtrix" function has the power to do all of the text mining above in one command.
```{r}
sms_dtm2 <- DocumentTermMatrix(comments_corpus_clean)
```

@@

##Data Preparation
Split data into training and testing sets, so that after Naive Bayes spam filter algorithm is built it can be applied to unseen data. Divide our data set into 75% training and 25% testing.

```{r}
.75 * 6551

.25 * 9129
```

This code assumes comments are random. **Probably want to try randomizing them.**
```{r}
comments_dtm_train <- sms_dtm2[1:4913, ]
comments_dtm_test <- sms_dtm2[4914:6551, ]
```

Save vectors labeling rows in the training and testing vectors
```{r}
comments_train_labels <- comments_raw[1:4913, ]$type
comments_test_labels <- comments_raw[4914:6551,]$type
```

##Visualization
Create a wordcloud of the frequency of the words in the dataset using the package "wordcloud".
```{}
wordcloud(comments_corpus_clean, max.words = 50, random.order = FALSE)
```

Compare wordclouds between 3 groups.
```{}
#TWO <- subset(comments_raw, type == "2_Writing")
THREE <- subset(comments_raw, type == "3_Technical")
FOUR <- subset(comments_raw, type == "4_Logic")

#wordcloud(TWO$text, max.words = 50, scale = c(3, 0.5))
wordcloud(THREE$text, max.words = 50, scale = c(3, 0.5))
wordcloud(FOUR$text, max.words = 50, scale = c(3, 0.5))
```

##Preparation for Naive Bayes
Remove words from the matrix that appear less than 5 times.
```{r}
comments_freq_words <- findFreqTerms(comments_dtm_train, 5)
str(comments_freq_words)
```

##Train Model, Predict, Evaluate
Use the e1071 package to implement Naive Bayes algorithm on the data, and predict whether a message is likely to be in group TWO, THREE, or FOUR. Evaluate the prediction with the actual data using a crosstable from the gmodels package.
```{r}
comments_classifier <- naiveBayes(comments_train, comments_train_labels)
comments_test_pred <- predict(comments_classifier, comments_test)
CrossTable(comments_test_pred, comments_test_labels, prop.chisq = FALSE, prop.t = FALSE, dnn = c('predicted', 'actual'))
```

Show the 10 most frequent words in the data:
```{r}
sack2 <- TermDocumentMatrix(comments_corpus_clean)
pack2 <- as.matrix(sack2)
snack2 <- sort(rowSums(pack2), decreasing = TRUE)
hack2 <- data.frame(word = names(snack2), freq=snack2)
head(hack2, 10)
```

And the 10 most frequent words from each class:
```{}
wordcloud(TWO$text, max.words = 10, scale = c(3, 0.5))
wordcloud(THREE$text, max.words = 10, scale = c(3, 0.5))
#wordcloud(FOUR$text, max.words = 10, scale = c(3, 0.5))
```
